### 2021-08-11 Manuscript.Rmd
Added table to output and imports variable correctly
Won't knit to the end due to negative variances error in lavaan

  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
  load(here("consistencies.rds"))

@@

>>>>

  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
  consistencies <- read_rds(here("consistencies.rds"))
  # create a vector of consistencies to be used as the diagonal in a table later
  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
  # paste together to create the output "alpha(omega)"
  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")

@@

`r desc_table`
